A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-12-11 paper/MSDS7330DBMSforGeospatiallyEnabledGame.tex
Rene's update
Changed some wording

The story is a science fiction story that places the player in the role of an explorer. The player finds himself exploring ruins on another world that once housed an advanced civilization and is charged with learning how the beings lived and what caused their disappearance. The player must then find objects, divided into three categories, that will divulge the necessary information about how this lost civilization lived and why it disappeared. Categories consist of Culture, Politics, and Technology and correspond to the nature of the player’s discoveries and tell the story of the civilization in tandem. For example, culture objects reveal how the civilization lived and what cultural tensions were present before they disappeared. Furthermore, the story arc of the civilization’s culture is told independently of the technology and politics story arcs, but with the common overarching plot of the civilization’s demise. An illustration of the story arc concept is presented below in \autoref{Tandem}.

@@

The important entities that the database must keep are: player, geospatial objects, stories and story-segments. We also need to know a player’s score in order to know what story segments the player has earned. Similarly, we need to know what objects have already been collected in order to not allow the player to collect them again.

@@

\subsubsection*{Stories}
As players make progress through the game, collecting more objects and reaching predefined score thresholds, new segments of the story unfold until the player reaches the end. This information is stored in the Segment Table, which contains the SegmentID, the score Threshold that the user should achieve to unlock the segment, and a text StoryFile that is displayed on the device.

>>>>

The story occurs in a science fiction setting that places the player in the role of an explorer. The player finds himself exploring ruins on another world that once housed an advanced civilization and is charged with learning how its members lived and what caused their disappearance. The player must then find objects, divided into three categories, that will divulge the necessary information about how this lost civilization lived and why it disappeared. Categories consist of Culture, Politics, and Technology and correspond to the nature of the player’s discoveries and tell the story of the civilization in tandem. For example, culture objects reveal how the civilization lived and what cultural tensions were present before they disappeared. Furthermore, the story arc of the civilization’s culture is told independently of the technology and politics story arcs, but with the common overarching plot of the civilization’s demise. An illustration of the story arc concept is presented below in \autoref{Tandem}.

@@

The important entities that the database must keep are: players, geospatial objects, stories and story-segments. We also need to know a player’s score in order to know what story segments the player has earned. Similarly, we need to know what objects have already been collected in order to not allow the player to collect them again.

@@

\subsubsection*{Stories and Story Segments}
As players make progress through the game, collecting more objects and reaching predefined score thresholds, new segments of the story unfold until the player reaches the end. This information is stored in the Segment Table, which contains the SegmentID, the score Threshold that the user should achieve to unlock the segment, and a text StoryFile that is displayed on the device.
